Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-19 ICML2019/main.tex
Fix lemma
move proof into apendix
fix problems in formula
fix typo
fix notation

\section{Private Mechanisms}
\label{sec_mechs}
\subsection{Calibrating noise w.r.t. $\ell_1$ norm}
We start off by presenting a mechanism based on the Laplace primitive.
The mechanism, denoted by {\color{red}{i think this macro has too many arguments}}($\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$),
simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
post-processing phase by {\color{red}{flooring}} and  truncating the noisy parameters so that they belong to the right interval.
In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
Since we are adding noise directly to the parameter, the sensitivity should be calibrated to $\ell_1$ of two Beta distributions:
$
   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
$,
i.e., proportional to the dimensionality.
  \begin{algorithm}
  \caption{$\lapmech$ in Beta-binomial model}
  \label{mech:lapmech}
  \begin{algorithmic}
  \REQUIRE observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
  \STATE \quad {\bf let} $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
  \STATE \quad {\bf let} $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
  % \RETURN $a_{k+1}$.
  \ENSURE $\betad(\tilde{\alpha}, \tilde{\beta})$
  \end{algorithmic}
  \end{algorithm}

@@

\subsection{Improving the sensitivity}
 The accuracy of $\lapmech$ can be reduced to a constant.
 Indeed, two adjacent data sets $\dataobs, \dataobs'$  induce posterior distributions -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ --
 whose parameters differ by at most 2 w.r.t $\ell_1$ norm. This because we can see the parameters of the distributions as an histogram.
 Hence, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.
 {\color{red} Notice that we are using the bounded notion of differential privacy \cite{????}.}
 \todo{why 1 in 2 dimensions?}
 We denote the mechanism which calibrates the noise to this smaller sensitivity as $\ilapmech$.
 $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces:
 $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0) $
 where $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in the Beta-binomial model and
 $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots,  \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}$
 with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}.
  \begin{algorithm}
  \caption{$\ilapmech$ in Dirichlet-multinomial model}
  \label{mech:ilapmech}
  \begin{algorithmic}
  \REQUIRE observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
  % \RETURN $a_{k+1}$.
  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
  \ENSURE $\dirichlet{\tilde{\valpha}}$
  \end{algorithmic}
  \end{algorithm}

\subsection{A new mechanism}
In this section, we explore a new mechanism which we denote by $\expmech$.
The idea is that $\expmech$ will sample and output a distribution with higher probability when
it is closer to the real posterior; importantly  \emph{closer} is measured using a metric over probability
distributions as opposed to a metric over the parameters that represent it. In this work we will
use the Hellinger distance, but this approach could be extended to other $f$-divergences. We will
start by describing how the mechanism works in the case of the Beta-Binomial model noticing that
the extension to the Dirichelet-Multinomial model is straightforward.
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
we define the follwing set  where the mechanism will sample from:
\[
  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs')\mid \dataobs' \in \{0,1\}^n\}.
\]
Notice that the above set reduces to:
\[
  \{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
\]
We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process on the observed data $\dataobs$
when the other two parameters, that is prior and likelihood, are fixed.

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$. This is just an attempt since local sensitivity is non-private. $\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\[
\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
\begin{equation}\label{eq:local_sensitivity_scoring}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation}

\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity}
\label{subsec_hexpmech}
In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and differential privacy simultaneously, by scaling the noise to a new sensitivity. We first define the new sensitivity we are going to use and then present the mechanism.
\begin{definition}
\label{def_gamma_smooth}
Given data set $\dataobs$ of size $n$, we define $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ is:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{definition}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\todo{Is it correct
$\lapmechPr{\dataobs}{\ldots}$? }
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

@@

\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
Thanks to the symmetry and triangle-inequality of the Hellinger
distance, we can simplify the local sensitivity.
\begin{lem}
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\end{lem}
\begin{proof}
For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
By taking the supremum, we conclude the statement of this lemma.
\end{proof}

>>>>

\section{Private Mechanisms}
\label{sec_mechs}
\subsection{Calibrating noise w.r.t. $\ell_1$ norm ($\lapmech$)}
We start off by presenting a mechanism based on the Laplace primitive.
The mechanism, denoted by {\color{red}{i think this macro has too many arguments}}($\lapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$),
simply adds Laplace noise to the parameters of the posterior distributions. The mechanisms also performs a
post-processing phase by {\color{red}{flooring}} and  truncating the noisy parameters so that they belong to the right interval.
In the case of the Beta-Binomial model the output produced is: $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0)$
with $\eta \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, where $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into
$[0,n]$. This mechanism is described by the pesudocode in Figure \ref{mech:lapmech}.\\
Since we are adding noise directly to the parameter, the sensitivity should be calibrated to $\ell_1$ of two Beta distributions:
$
   \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1
$,
i.e., proportional to the dimensionality.
  \begin{algorithm}
  \caption{$\lapmech$ in Beta-binomial model}
  \label{mech:lapmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \{0,1\}^n$, inference algorithm: $\bysinfer$, 
  prior: $\betad(\alpha, \beta)$, likelihood: $\binomial{n}{\theta}$, $\epsilon$
  \STATE \quad {\bf let} $\betad(\alpha', \beta') = \bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$.  
  \STATE \quad  $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
  \STATE \quad  $\tilde{\alpha}=\alpha + \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ 
  \STATE \quad  $\tilde{\beta}=\beta + n - \lfloor{(\alpha' - \alpha) + \eta}\rfloor^n_0$ \\
  % \RETURN $a_{k+1}$.
  \noindent {\bf return} $\betad(\tilde{\alpha}, \tilde{\beta})$
  \end{algorithmic}
  \end{algorithm}

@@

\subsection{Improving the sensitivity ($\ilapmech$)}
 The accuracy of $\lapmech$ can be reduced to a constant.
 Indeed, two adjacent data sets $\dataobs, \dataobs'$  induce posterior distributions -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ --
 whose parameters differ by at most 2 w.r.t $\ell_1$ norm. This because we can see the parameters of the distributions as an histogram.
 Hence, it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions.
 {\color{red} Notice that we are using the bounded notion of differential privacy \cite{????}.}
 \todo{why 1 in 2 dimensions?}
 We denote the mechanism which calibrates the noise to this smaller sensitivity as $\ilapmech$.
 $\ilapmech(\dataobs,\bysinfer, \mathsf{prior}, \mathsf{likelihood}, \epsilon)$ produces:
 $\betad(\alpha +  \lfloor{\Delta \alpha + \eta}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + \eta}\rfloor^n_0) $
 where $\eta \thicksim \lap{0}{\frac{1}{\epsilon}}$ in the Beta-binomial model and
 $\dirichlet{\alpha_1 +  \lfloor{\Delta \alpha_1 + \eta_1}\rfloor^n_0, \cdots,  \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + \eta_i}\rfloor^n_0 \rfloor^n_0}$
 with $\eta_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model. Details are shown in Figure \ref{mech:ilapmech}.
  \begin{algorithm}
  \caption{$\ilapmech$ in Dirichlet-multinomial model}
  \label{mech:ilapmech}
  \begin{algorithmic}
  \INPUT observed data set $\dataobs \in \mathcal{X}^n$, inference algorithm: $\bysinfer$, 
  prior: $\dirichlet{\valpha}$, likelihood: $\multinomial{n}{\vtheta}$, $\epsilon$
  \STATE \quad {\bf let} $\dirichlet{\valpha'} = \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)$, $k = |\mathcal{X}|$.
  \STATE \quad {\bf Initialize} a vector $\tilde{\valpha} = (0, \dots, 0 )$ of $k$ dimensions .
  \STATE \quad {\bf For} $i = 1 \dots (k - 1)$:
  \STATE \quad \quad  {\bf let} $\eta \sim \lap{0}{\frac{2}{\epsilon}}$.
  \STATE \quad \quad  $\tilde{\alpha_i}=\alpha_i + \lfloor{(\alpha_i' - \alpha_i) + \eta}\rfloor^n_0$ 
  % \RETURN $a_{k+1}$.
  \STATE \quad $\tilde{\alpha_k} = \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{(\alpha_i' - \alpha_i) + \eta_i}\rfloor^n_0 \rfloor^n_0$
  \STATE {\bf return} $\dirichlet{\tilde{\valpha}}$
  \end{algorithmic}
  \end{algorithm}

\subsection{A new mechanism}
In this section, we explore a new mechanism which we denote by $\expmech$.
The idea is that $\expmech$ will sample and output a distribution with higher probability when
it is closer to the real posterior; importantly  \emph{closer} is measured using a metric over probability
distributions as opposed to a metric over the parameters that represent it. In this work we will
use the Hellinger distance, but this approach could be extended to other $f$-divergences. We will
start by describing how the mechanism works in the case of the Beta-Binomial model noticing that
the extension to the Dirichelet-Multinomial model is straightforward.
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$,
we define the follwing set  where the mechanism will sample from:
\[
  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs)\mid \dataobs \in \{0,1\}^n\}.
\]
Notice that the above set reduces to:
\[
  \{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
\]
We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process on the observed data $\dataobs$
when the other two parameters, that is prior and likelihood, are fixed.

\subsubsection{Exponential Mechanism with Hellinger Distance Metric ($\expmech$)}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity ($\lexpmech$)}
\label{subsec_emls}
In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$. This is just an attempt since local sensitivity is non-private. $\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\[
\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
\begin{equation}\label{eq:local_sensitivity_scoring}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation}

Thanks to the symmetry and triangle-inequality of the Hellinger
distance, we can simplify the local sensitivity.
\begin{lem}
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\end{lem}

(Proof is in Appendix IV.)

\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity ($\hexpmech$)}
\label{subsec_hexpmech}
In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and differential privacy simultaneously, by scaling the noise to a new sensitivity. We first define the new sensitivity we are going to use and then present the mechanism.
\begin{definition}
\label{def_gamma_smooth}
Given data set $\dataobs$ of size $n$, we define $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ is:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{definition}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

@@

\begin{align*}
&
\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{2}} - e^{- \frac{\epsilon (t + 1)}{2}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{2}} - e^{\frac{\epsilon (t)}{2}}) & t < 0
\end{cases}
\end{align*}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

@@

% \subsection{Efficiency Evaluation}
% \label{subsec_effi}
% %The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
% %\[
% %LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
% %\]
% Thanks to the symmetry and triangle-inequality of the Hellinger
% distance, we can simplify the local sensitivity.
% \begin{lem}
% \[
% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
% \]
% \end{lem}
% \begin{proof}
% For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
% \begin{align*}
% &\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
% & = 
% \begin{cases}
% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer(\dataobs), r) & \text{negative case}
% \end{cases}\\
% & \leq 
% \begin{cases}
% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
% \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
% \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
% \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
% \end{cases}\\
% &= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
% \end{align*}
% The equality holds if $r = \bysinfer(\dataobs)$ or $r = \bysinfer(\dataobs')$.
% Hence, we conclude the statement of this lemma.
% \end{proof}
